A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-06-10 doc/large_strain.tex
remove double Bibliography
improve Intro

The paper is organized as follows:
In Section \ref{sec:theory} we briefly introduce the partial differential equations used in  finite-strain solid mechanics.
Sections \ref{sec:fe} cover the finite element discretization.
In \ref{sec:mf} we describe the different matrix-free operator implementations that are evaluated in this study.
Section \ref{sec:framework} provides details of the numerical framework with which this study is implemented,
where we also propose a method by which to construct level tangent operators for
a geometric multigrid preconditioner that is suitable for the matrix-free implementation of finite-strain hyperelasticity.
%
The performance of the matrix-free operator and the geometric multigrid preconditioner is compared to the matrix-based implementation with an algebraic multigrid preconditioner for a representative numerical example of a heterogeneous hyperelastic material simulated in two and three dimensions in Section \ref{sec:example}.
Lastly, the results are summarized in Section \ref{sec:summary}.

@@

\ifijnme
\bibliographystyle{wileyj}
\else
\section*{Bibliography}
\bibliographystyle{elsarticle-num}
\fi

>>>>

The paper is organized as follows:
In Section \ref{sec:theory} we briefly introduce the partial differential equations used in finite-strain solid mechanics,
while section \ref{sec:fe} covers the finite element discretization.
In Section \ref{sec:mf} we describe the different matrix-free operator implementations that are evaluated in this study.
Section \ref{sec:framework} provides details of the numerical framework with which this study is implemented,
where we also propose a method by which to construct level tangent operators for
a geometric multigrid preconditioner that is suitable for the matrix-free implementation of finite-strain hyperelasticity.
%
The performance of the matrix-free operator and the geometric multigrid preconditioner is compared to the matrix-based implementation with an algebraic multigrid preconditioner for a representative numerical example of a heterogeneous hyperelastic material simulated in two and three dimensions in Section \ref{sec:example}.
Lastly, the results are summarized in Section \ref{sec:summary}.

@@

\ifijnme
\bibliographystyle{wileyj}
\else
%\section*{Bibliography}
\bibliographystyle{elsarticle-num}
\fi
